A Partitioning Algorithm for Maximum Common Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-15 paper/paper.tex
More writing about the experiments

\paragraph{No vertex labels, no edge labels, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis)
against number of problem instances solved (y-axis).  There are five contours:
the clique encoding \cite{DBLP:conf/cp/McCreeshNPS16}, CP-FC
\cite{DBLP:conf/cp/NdiayeS11}, \McSplit\, AND TWO OTHERS.  WE NEED CITATIONS
FOR THESE AND ALSO NEED TO CLEAN UP THE LABELS ON THE GRAPHS.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2000 of the 4110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3506 instances that
could be solved by at least one of \McSplit, CP-FC and clique in less than than
1000 seconds, there were only 126 instances on which \McSplit\ was not strictly
faster than the other two solvers.

\paragraph{Vertex labels, edge labels, directed}
Cumulative run times for this class of instances are in \cref{figure:33ved-cumulative}.
Again, \McSplit\ is over an order of magnitude faster than the best CP algorithm,
which is CP-MAC in this case.  The clique encoding, however, outperforms the other
algorithms on these labelled instances, except in the easy region at the left
of the graph.

\paragraph{Vertex labels, no edge labels, undirected} are in
FIGURE REMOVED
%\cref{figure:33v-cumulative},
and are not in other papers so we should omit this unless we see something interesting.

\paragraph{Vertex labels,  edge labels, undirected} are in
FIGURE REMOVED
%\cref{figure:33ve-cumulative},
and are not in other papers so we should omit this unless we see something interesting.

\paragraph{No Vertex labels, no edge labels, undirected, connected} are in \cref{figure:plain-connected-cumulative}.

\paragraph{Vertex labels, edge labels, undirected, connected} are in \cref{figure:33ve-connected-cumulative}.

\paragraph{Large subgraph isomorphism instances} are in \cref{figure:sip-cumulative}.

\paragraph{Compared to CP FC} Nodes are in
FIGURE REMOVED
%\cref{figure:plain-james-versus-cp-fc-nodes-scatter}
and \cref{figure:33ved-james-versus-cp-fc-nodes-scatter}.

\paragraph{Nodes compared to kdown on SIP} are in \cref{figure:sip-james-versus-kdown-nodes-scatter}.

@@

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{Cumulative run times, SIP instances}\label{figure:sip-cumulative}
\end{figure}

%\begin{figure}
%    \centering
%    \includegraphics*{gen-graph-plain-james-versus-cp-fc-nodes-scatter.pdf}
%    \caption{MCS Plain instances, James vs CP-FC, Nodes (TODO?? heatmapify this
%    and exclude timeouts)}\label{figure:plain-james-versus-cp-fc-nodes-scatter}
%\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, James vs
    CP-FC, Nodes (TODO?? heatmapify this and exclude
    timeouts)}\label{figure:33ved-james-versus-cp-fc-nodes-scatter}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-sip-james-versus-kdown-nodes-scatter.pdf}
    \caption{SIP instances, James vs kdown, Nodes (TODO?? heatmapify this and exclude
    timeouts)}\label{figure:sip-james-versus-kdown-nodes-scatter}
\end{figure}

@@

\newpage
\bibliographystyle{named}
\bibliography{paper}

>>>>

@@

\paragraph{No vertex or edge labels, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis)
against number of problem instances solved (y-axis).  There are five contours:
the clique encoding \cite{DBLP:conf/cp/McCreeshNPS16}, CP-FC
\cite{DBLP:conf/cp/NdiayeS11}, \McSplit\, AND TWO OTHERS.  WE NEED CITATIONS
FOR THESE AND ALSO NEED TO CLEAN UP THE LABELS ON THE GRAPHS.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2000 of the 4110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3506 instances that
could be solved by at least one of \McSplit, CP-FC and clique in less than than
1000 seconds, there were only 126 instances on which \McSplit\ was not strictly
faster than the other two solvers.

\paragraph{Vertex and edge labels, directed} Cumulative run times for this
class of instances are in \cref{figure:33ved-cumulative}.  Again, \McSplit\ is
over an order of magnitude faster than the best existing CP algorithm, which is
CP-MAC in this case.  The clique encoding outperforms the other
algorithms---including \McSplit---on these labelled instances, except in the
very easy region of instances that can be solved in well under 100 ms.

\paragraph{No Vertex or edge labels, undirected, connected} are in
\cref{figure:plain-connected-cumulative}.  These results are very similar to
the corresponding experiment in which the subgraph is not required to be
connected (\cref{figure:plain-cumulative}).

\paragraph{Vertex and edge labels, undirected, connected} For the labelled,
connected case, clique slightly outperforms \McSplit\ on harder instances
(\cref{figure:33ve-connected-cumulative}).  The gap between the two algorithms
is narrow; indeed, the cumulative curve for \McSplit\ briefly rises above
the curve for clique at a runtime just below 100 seconds.

@@

\paragraph{Large subgraph isomorphism instances} We also ran the algorithms on
a set of 5725 larger instances used in recent studies of subgraph
isomorphism~\cite{thelionpaper} and maximum common
subgraph~\cite{UpcomingAAAIPaper}.  This benchmark set includes real-world
graphs, along with graphs generated using several random models.  Pattern
graphs range from 4 vertices to 900 with a median of 80; target graphs range
from 10 vertices to 6671 with a median of 561.  Cumulative runtimes including
top-down algorithm from~\cite{UpcomingAAAIPaper} which was the previous state
of the art for this benchmark, are in \cref{figure:sip-cumulative}.  This is a
challenging set of instances, and more than half of the instances cannot be
solved within a timeout of 1000 seconds by any of the solvers. \McSplit\ is the
strongest solver overall for these instances.

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{Cumulative run times, SIP instances}\label{figure:sip-cumulative}
\end{figure}

\paragraph{CP-FC and \McSplit\ search nodes on MCS instances}
\cref{figure:33ved-james-versus-cp-fc-nodes-scatter} shows one point per instance,
with search nodes visited by CP-FC on the horizontal axis and search nodes visited
by \McSplit\ on the vertical axis.  There is a strong correlation, which reflects
the similarity of the search space explored by the two algorithms.  \McSplit\
tends to explore slightly fewer search nodes than CP-FC, because the label-classes
allow us to (cheaply) compute a very good heuristics for variable selection.

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-33ved-james-versus-cp-fc-nodes-scatter.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, James vs
    CP-FC, Nodes (TODO?? heatmapify this and exclude
    timeouts)}\label{figure:33ved-james-versus-cp-fc-nodes-scatter}
\end{figure}

\paragraph{kdown and \McSplit\ search nodes on SIP instances}
\cref{figure:sip-james-versus-kdown-nodes-scatter} shows the number of search
nodes taken by kdown and \McSplit\ on each instance.  Although \McSplit\ is the
faster algorithm overall, it explores more search nodes than kdown for most instances.
The scatter plot has a concentration of points around the line $y=2x$. We conjecture
that the two algorithms explore very similar search trees for instances close to this
line.

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-sip-james-versus-kdown-nodes-scatter.pdf}
    \caption{SIP instances, James vs kdown, Nodes (TODO?? heatmapify this and exclude
    timeouts)}\label{figure:sip-james-versus-kdown-nodes-scatter}
\end{figure}

@@

\bibliographystyle{named}
\bibliography{paper}
